Comparative vaccine effectiveness (ChAdOx1 versus BNT162b2) in Health and Social Care workers

### 2021-09-09 analysis/report/effectiveness_report_comparemodels.Rmd
remove second dose censoring

cat("  \n\n")
# print(glue("### COVID-19 A&E attendance"), "  \n")
# print(glue("#### Unadjusted"), "  \n")
# print_plots_km("covidemergency")
# print(glue("#### Cox"), "  \n")
# print_plots_effects("covidemergency", "cox", "0")
# print(glue("#### PLR, piecewise"), "  \n")
# print_plots_effects("covidemergency", "plr", "0")
# print(glue("#### PLR, spline"), "  \n")
# print_plots_spline("covidemergency", "0")
# print_plots_adjsurv("covidemergency", "0")
# print_plots_diff("covidemergency", "0")

>>>>

cat("  \n\n")
print(glue("### COVID-19 A&E attendance"), "  \n")
print(glue("#### Unadjusted"), "  \n")
print_plots_km("covidemergency")
print(glue("#### Cox"), "  \n")
print_plots_effects("covidemergency", "cox", "0")
print(glue("#### PLR, piecewise"), "  \n")
print_plots_effects("covidemergency", "plr", "0")
print(glue("#### PLR, spline"), "  \n")
print_plots_spline("covidemergency", "0")
print_plots_adjsurv("covidemergency", "0")
print_plots_diff("covidemergency", "0")
